Training an Agent on Brainwaves

### 2019-10-18 ErrP.tex
Rewrote intro

% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
\IEEEPARstart{T}{he} effectiveness of today's human–machine interaction is limited by a communication bottleneck as operators are required to translate high-level concepts into a machine-mandated sequence of instructions \cite{CURSOR-CONTROL-PAPER}. This work tackles directly this problem by exploring the use of brain signals as an interface between human and computer, overcoming this limitation by enabling the control of the system without explicit communication from the user.

Using reinforcement learning with reward signals based on brain activity, recorded by an EEG-based BCI system during the task execution, in order to train an agent has been explored in previous research. The paper \cite{ROBOT-CONTROL-PAPER} has successfully demonstrated that a robot can be controlled by obtaining the reward from brain activity generated while observing the robot solving a task. The present project applies a similar process for making a virtual agent improve its performance using electroencephalography (EEG) signals as feedback for a reinforcement learning algorithm. The idea is that subjects observing a simple simulated system can train such system using only error-related potentials (ErrP) that can be identified in their brain signals. The detection of ErrP signals has been explored in the publication \cite{EERP-PAPER} which describes the methods that are used in order to identify this specific potential from EEG signals.

In recent years reinforcement learning has seen a come-back. This is mainly because of DeepBrain's AlphaGo who was the first to reach superhuman proficiency in challenging domains, when it won the complex game Go against several world champions. In 2015 AlphaGo won 5 matches against 3-times European Champion, Mr Fan Hui. AlphaGo then went on to compete against Mr Lee Sedol, winner of 18 world titles and considered to be the greatest player until then, and won 4 out of 5 matches in 2016 \cite{ALPHA-GO}.

@@

In Section I, in Section II and Results and conclusions are exposed at the end.

\section{Materials and Methods}

The project consists of collecting signals from a person's brain while they are watching a game where the agent has knowledge of the way it's played but not how to win it. Hence, the agent can learn using the person's feedback to get better at the game. This section describes the process of obtaining the person's brain signals and how they are used to make the agent improve it's performance.

@@

The experimental procedure is summarized in Figure \ref{diag:complete_flow}. The core of the procedure is the retrieval of the subject's brain activity. This process is called brainwave session. In order to fetch this data, subjects use a wireless digital EEG device during the experiment. Once the subject has the headset on, a set up procedure is executed as described in Section \ref{cognitive_experiment_details} using a program called g.NeedAcceess to do an impedance check and to visually inspect the EEG signals in order to check if it's correctly applied. Subsequently, the OpenVibe Acquisition Server program is launched and configured. This program is part of the OpenVibe platform \cite{OPEN-VIBE-PAPER} and has the responsibility of receiving the signals data from the headset and stimulus information from the game and transfers it to the OpenVibe Designer application. After this step, the Game and the OpenVibe Designer programs are launched and configured to communicate with the previously mentioned acquisition server. Once the subject is ready the computer is positioned in front of them and the brainwave session starts. A brainwave session consists of several experiences, each of them being a game run, and it uses a pseudo-random function to determine the agent's movements. The system is described in more detail in Section \ref{cognitive_experiment_system} and the brainwave session in Section \ref{cognitive_experiment_details}. Once the experimental procedure is completed, the game state information and the signals data with the stimuli channel information of each run are stored. For each run, the signals and stimulus information are then passed to the classification module that uses them to train the classifier. The classification step is covered in detail in Section \ref{signal_processing_and_classification}. After this step is finished, the game movements and the trained classifier are used to update a Q-Table for each experience. Lastly, the calculated Q-Table is used to test if the agent has boosted its performance while playing the game. This module is explained in Section \ref{q_learning_step}.

\subsection{Cognitive Game experiment}
This section details the game system characteristics, the brainwave session process and the retrieval and analysis of the generated data from the subjects interaction with the system.

\label{cognitive_experiment_system}{
The system consists of a $5x5$ grid where there are two lights, one representing the current position of the agent, and the other one representing the goal, shown in figure  \ref{fig:game_representation}. The objective of the system is for the agent to reach the goal. The light representing the goal remains static at the bottom-right position of the grid, while the one representing the position of the agent always starts at the upper-left position of the grid. The grid is represented by circular spots with a black background. The agent's position has a blue light, the goal position has a green light, and the rest of cells are represented with grey spots. When the agent reaches the goal, the position where the agent and the goal are located turns red, showing that the experience has ended. There are four possible movements that the agent can perform: it can go upwards, downwards, towards the left and towards the right, as long as the move doesn't make the agent leave the grid. The movement direction is selected randomly and is executed once every 2 seconds. When the experience ends, there is a pause of 5 seconds before the next experience starts. The experience is designed for it to be evident whenever there is an error (when the agent moves away from the objective) so the subject can notice it immediately after the stimulus is presented, possibly triggering a cognitive response.

@@

\section{Calibration}

@@

The goal of this module is to build a classifier that is able to identify whether the action taken by the agent is an error or not. It is developed in Python using the \href{https://mne-tools.github.io/0.11/index.html}{MNE} environment \cite{MNE-PYTHON}, which is a package designed specifically for processing EEG and MEG data, and the machine learning library \href{https://scikit-learn.org/stable/}{Scikit-Learn}.

@@

>>>>

% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
\IEEEPARstart{T}{he} effectiveness of today's human–machine interaction and artificial intelligence is limited by a communication bottleneck as humans are required to translate high-level concepts into a machine-mandated sequence of instructions \cite{CURSOR-CONTROL-PAPER}.   This work tackles this problem by exploring the use of brain signals as an interface between human and computer, trying to overcome this limitation by providing information to the system without explicit communication from the user.  This information is used to make a gaming agent improve its operational performance using electroencephalography (EEG) signals as feedback of the performed task from an observational human critic. The idea is that subjects observing a computer game play can train the gaming agent using only electrophisiological signals called Error-related Potentials (ErrP) that can be identified from their brain signals.

Error-related Potentials are signal components that can be found on EEG traces and are elicited when a subject is aware of the presence of un unexpected outcome, which she identifies as an error.  It is currently an extensive area of research in the neuroscience community~\cite{Chavarriaga2014} PAPER NEURO.  They can detected by signal processing and machine learning techniques~\cite{EERP-PAPER} and they are also used in Brain-Computer Interfaces (BCI) to implement or enhance artificial communication channels~\cite{Chavarriaga2014}.

In order to train the agent, a natural solution for this scenario comes handy from the field of Artificial Intelligence: Reinforcement Learning (RL). Recently, this technique has seen a come-back. Nonneglected is the influence of DeepBrain's AlphaGo project, which was the first to reach superhuman proficiency when it won the complex game Go against several world champions. By using variants of this technique, in 2015 AlphaGo won 5 matches against 3-times European Champion, Mr Fan Hui. AlphaGo then went on to compete against Mr Lee Sedol, winner of 18 world titles and considered to be the greatest player until then, and won 4 out of 5 matches in 2016 \cite{ALPHA-GO}.

Previous research has explored the usage of RL with reward signals based on brain activity, recorded by an EEG-based BCI system during the task execution. The paper \cite{ROBOT-CONTROL-PAPER} has successfully demonstrated that a robot can be controlled by obtaining a reward signal from brain activity of a person which is observing the robot solving a task   OTHERS WORKS.   In the same line, the objective of this work is to use the information extracted from brainwaves to enhance the performance of a gaming agent, replicating and extending those results.

@@

In Section \ref{section:materials} the general layout of the cognitive game experiment is described. Section \ref{section:calibration} outlines the processing pipeline used to detect ErrP components. The following Section \ref{section:classification} describes the classification algorithm and their parameters.   Results and conclusions are exposed at the end.

\section{Materials and Methods}
\label{section:materials}

This experiment consists of collecting signals from a person's brain while they are watching a game where the agent knows the game rules but not how to win it. Hence, the agent can learn the winning strategy using the person's feedback to improve its own performance. This section describes the process of obtaining the person's brain signals and how they are used to make the agent more efficient.

@@

The experimental procedure is summarized in Figure \ref{diag:complete_flow}. The core of the procedure is the retrieval of the subject's brain activity. This process is called brainwave session. In order to fetch this data, subjects use a wireless digital EEG device during the experiment (g.Mobilab, g.Tec, Austria). Once the subject has the headset on, a set up procedure is executed to implement an impedance check and to visually inspect the EEG signals in order to verify if it the electrophisiological interface is generating valid data. Subsequently, the OpenVibe Acquisition Server, from the OpenVibe platform~\cite{OPEN-VIBE-PAPER}, is launched and configured. This program has the responsibility of receiving the signal data from the headset and any event information from the game and transfers it to the OpenVibe Designer application. After this step, the Game and the OpenVibe Designer programs are launched and configured to communicate with the previously mentioned acquisition server. Once the subject is ready, a computer screen is positioned in front of her and the brainwave session starts. A brainwave session consists of several experiences, each one being a game run, and it uses a pseudo-random function to determine the agent's movements. The system is described in more detail in Section \ref{cognitive_experiment_system} and the brainwave session in Section \ref{cognitive_experiment_details}. Once the experimental procedure is completed, the game state information and the signal data with the game event information of each run are stored. For each run, the signals and stimulus information are then passed to the classification module that uses them to train the classifier. The classification step is covered in detail in Section \ref{signal_processing_and_classification}. After this step is finished, the game movements and the trained classifier are used to update a Q-Table for each experience. Lastly, the calculated Q-Table is used to test if the agent has boosted its performance while playing the game. This module is explained in Section \ref{q_learning_step}.

\subsection{Cognitive Game experiment}
\label{cognitive_experiment_details}
%This section details the game system characteristics, the brainwave session process and the retrieval and analysis of the generated data from the subjects interaction with the system.

\label{cognitive_experiment_system}{
The game parsimoniously consists of a $5x5$ grid of grey circular spots with a black background.  A blue spot indicates current position of the agent whereas a a green spot represents the goal, as shown in figure  \ref{fig:game_representation}. The objective of the system is for the agent to reach the goal. The circular spot representing the goal remains static at the bottom-right position of the grid, while the one representing the position of the agent always starts at the upper-left position of the grid.  When the agent reaches the goal, the position where the agent and the goal are located turns red, showing that the experience has ended. There are four possible movements that the agent can perform: it can go upwards, downwards, towards the left and towards the right, and those moves are bounded to avoid the agent from leaving the grid. The movement direction is selected randomly and is executed once every 2 seconds.  When the experience ends, there is a pause of 5 seconds before the next experience starts. Each time an agent moves, it is considered as a stimulus to the observational human critic.  The experience is designed for it to be evident whenever there is an error (i.e. the agent moves away from the objective) so the subject can notice it immediately after the stimulus is presented, possibly triggering the expected cognitive response, which can be imprinted as an ErrP component within the EEG stream.

@@

\section{Calibration}
\label{section:calibration}

@@

To aid in detecting the ErrP response, an offline processing pipeline and classifier is constructed to identify whether the action taken by the agent is an error or not. It is developed in Python using the \href{https://mne-tools.github.io/0.11/index.html}{MNE} platform \cite{MNE-PYTHON}, which is a package designed specifically for processing EEG and MEG data, and the machine learning library \href{https://scikit-learn.org/stable/}{Scikit-Learn}.

@@

Enfatizar la idea de que la mejor métrica de la propia detección está dada por la propia capacidad del agente de minimizar su tarea, que hay un flujo de información que involucra la propia percepción de la persona.
